\documentclass{beamer}
\usetheme{Madrid}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\title{Digital Analysis of Pausanias}
\author{COMP3420 Documentation}
\date{\today}
\begin{document}
\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Project Overview}
  \begin{itemize}
    \item Pausanias' \emph{Description of Greece} (2nd~c.~CE) mixes myth and travelogue.
    \item Scholars debate how critically Pausanias reports local traditions.
    \item This project provides tools to analyse the text using modern NLP.
    \item Pipeline: import \textrightarrow{} annotate \textrightarrow{} model \textrightarrow{} visualise.
  \end{itemize}
\end{frame}

\begin{frame}{Data Ingestion}
  \begin{itemize}
    \item Raw text segmented as passages with IDs (e.g., \texttt{1.1.1}).
    \item \texttt{pausanias\_importer.py} loads passages into a SQLite database.
    \item \texttt{translate\_pausanias.py} uses the OpenAI API to produce English translations.
  \end{itemize}
\end{frame}

\begin{frame}{Proper Noun Extraction}
  \begin{itemize}
    \item \texttt{extract\_proper\_nouns.py} queries the API with tool calls to identify people, places, and deities.
    \item Results stored with entity type and canonical form.
    \item These nouns act as stopwords and later form a co--occurrence network.
  \end{itemize}
\end{frame}

\begin{frame}{Mythic vs Historical \& Skepticism}
  \begin{itemize}
    \item \texttt{mythic\_sceptic\_analyser.py} labels each passage:
          \begin{enumerate}
            \item Does it reference mythic time or real history?
            \item Does Pausanias express scepticism?
          \end{enumerate}
    \item Metadata on token usage is recorded for reproducibility.
  \end{itemize}
\end{frame}

\begin{frame}{Machine Learning Models}
  \begin{itemize}
    \item \texttt{find\_predictors.py} builds logistic regression models using \texttt{scikit\-learn}.
    \item TF--IDF features highlight words associated with mythic content or scepticism.
    \item COMP3420 students will recognise this pipeline of vectorisation and classification.
  \end{itemize}
\end{frame}

\begin{frame}{Network Analysis}
  \begin{itemize}
    \item \texttt{analyse\_noun\_network.py} constructs a graph with NetworkX.
    \item Nodes: proper nouns; edges: co--occurrence in passages.
    \item Centrality metrics (degree, betweenness, PageRank) reveal key figures like Apollo or Athens.
    \item Output visualisations use D3.js in an interactive web page.
  \end{itemize}
\end{frame}

\begin{frame}{Website Generation}
  \begin{itemize}
    \item Modular code in \texttt{website/} creates a static site showing analyses.
    \item Passages are highlighted with predictive words, translated text, and lists of proper nouns.
    \item \texttt{cronscript.sh} can run the entire pipeline daily and sync results to a server.
  \end{itemize}
\end{frame}

\begin{frame}{Takeaways}
  \begin{itemize}
    \item Combines classical scholarship with modern NLP methods you know from scikit--learn and Keras.
    \item Encourages reflection on how language signals mythic storytelling and scepticism in ancient texts.
    \item Code is modular and can be adapted for other corpora or further analyses.
  \end{itemize}
\end{frame}

\end{document}
